Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-22 CMSAC_presentation/CMSAC_reveal_js.qmd
Image Size fix

::::: columns
::: {.column width="48%"}
```{r}
#| echo: false
html_df
```
:::

::: {.column width="%48%"}
```{r}
#| echo: false
#| out.width: "100%"
knitr::include_graphics("simulation_example.png")
```
:::
:::::

>>>>

::::: columns
::: {.column width="37%"}
```{r}
#| echo: false
html_df
```
:::

::: {.column width="63%"}
```{r}
#| echo: false
#| out-width: "125%"
#| out-length: "150%"
#| fig-width: 8
#| fig-height: 16
knitr::include_graphics("simulation_example.png")
```
:::
:::::
